---
title: "APM1110 - FA 6 - Dacanay"
output: github_document
---

#### I. Geometric Distribution. Provide an R code for the geometric distribution. The geometric distribution is a probability distribution that models the number of trials required to achieve the first success in a sequence of Bernoulli trials, where each trial has a constant probability of success.


#### 1. Set the probability of success:  p <- 0.2
```{r}
p <- 0.2
```


#### 2. Generate 1000 random variables from the geometric distribution.
```{r}
x <- rgeom(1000, prob = p) + 1
```


#### 3. Calculate some basic statistics:
```{r}
# Calculate some basic statistics
mean_x <- mean(x)
var_x <- var(x)
sd_x <- sd(x)
```

##### MEAN:
```{r}
mean_x
```
##### VARIANCE:
```{r}
var_x
```

##### VARIANCE:
```{r}
var_x
```

##### STANDARD DEVIATION:
```{r}
sd_x
```


#### 4. Print the results in item 3 with the following output (string)
##### Number of trials required to achieve first success:
```{r}
x
```
##### MEAN (in 2 decimal places):
```{r}
mean_x_rounded <- round(mean_x, 2)
mean_x_rounded
```
##### VARIANCE (in 2 decimal places):
```{r}
var_x_rounded <- round(var_x, 2)
var_x_rounded
```
##### STANDARD DEVIATION (in 2 decimal places):
```{r}
sd_x_rounded <- round(sd_x, 2)
sd_x_rounded
```


#### 5. Plot the histogram of the results.
```{r}
hist(x, main = "Number of Trials Required to Achieve First Success",
     xlab = "Number of Trials", ylab = "Frequency",
     col = "blue", border = "white")
```



#### II. Hypergeometric Distribution.  Consider a plant manufacturing IC chips of which 10% are expected to be defective. The chips are packed in boxes for export. Before transportation, a sample is drawn from each box. Estimate the probability that the sample contains more than 10% defectives, when:

Assign values
```{r}
# Population size
p_size_40 <- 40
p_size_5000 <- 5000

# Sample size
sample_size <- 10

# Defective Percentage
p_size_40_defective <- p_size_40 * 0.1
p_size_5000_defective <- p_size_5000 * 0.1

k <- 1
```

#### 1. A sample of 10 is selected from a box of 40
```{r}
p_40 <- 1 - phyper(k, p_size_40_defective, p_size_40-p_size_40_defective, sample_size)
```
##### ANSWER:
```{r}
p_40_rounded <- round(p_40, 4)
p_40_rounded
```
The probability that the sample contains more than 10% defectives when a sample of 10 is selected from a box of 40 is $0.2559$ or $25.59$%.


#### 2. A sample of 10 is selected from a box of 5000.
```{r}
p_5000 <- 1 - phyper(k, p_size_5000_defective, p_size_5000-p_size_5000_defective, sample_size)
```
##### ANSWER:
```{r}
p_5000_rounded <- round(p_5000, 4)
p_5000_rounded
```
The probability that the sample contains more than 10% defectives when a sample of 10 is selected from a box of 5000 is $0.2639$ or $26.39$%.











